Deciding to Disclose

### 2015-11-12 Background.tex
Substantive background back in

%!TEX root = disclosure_game.tex
%Rewrite all of this, ditch the alcohol stuff altogether. Any really key can be woven in elsewhere (discussion)
\section{Previous Research}

@@

This section presents a brief overview of previous work relating to the theoretical backdrop to this approach, addressing in turn signalling games, normative decision theory, heuristic decision making, and descriptive decision theory.

\subsection{Signalling Games}

The majority of classical game theory focuses on strategic decision making, in scenarios where all players have complete information about all aspects of the game. An alternative, perhaps more common situation, is that players have incomplete information, i.e. their knowledge of the state of the world is in some way deficient. \citet{Harsanyi1967} introduced the concept of a Bayesian game, resolving the problems introduced by the incomplete information scenario by allowing the possible variations on the rules to be treated as subgames. This adds an additional player - nature, to the game, where nature takes the first move thereby deciding which subgame is played. Nature is assumed to make their move by lottery, and where the probability distribution governing the lottery is known to all players this permits the game to be formulated as one of complete information.

Here, we are specifically interested in signalling games \citep{Spence1973,Kreps1987}, where one player holds some private information which may be communicated (or not) by means of a signal.
This basic form has been widely applied, with substantial interest in what conditions permit honest signalling as Nash equilibria or \acp{ESS}. \citet{Grafen1990}, following from a suggestion by \citet{Zahavi1975}, proposed that if signals intended to indicate mate quality exacted a cost on the signaller (e.g. peacock tail feathers), then honest signalling would constitute an \ac{ESS}. Similar results have also been demonstrated in a game of job market signalling, where signal cost was differentiated by type \citep{Spence1973}. 
Costly signalling has also been suggested as an explanation of behaviour that at first glance appears counter intuitive, for example \citet{Godfray1991} applied the idea to the food solicitation behaviour of chicks, where a stronger signal (i.e. more, or louder chirping) carries a risk of being eaten by predators. Moving beyond animal behaviour, \citet{Sosis2003} considered the implications of ritual behaviour, in the context of religion, representing a costly signal, an idea subsequently extended by \citet{Henrich2009} to include cultural transmission, and \citet{Wildman2011} to introduce group differentiation.

Other work augments the signalling game model, for example \citet{Austen-Smith2005} add a second `peer group' audience signalling game to the original \citeauthor{Spence1973} game in an effort to explain poor academic performance in some social groups, with some subsequent empirical support for the idea from \citet{Jr2010}. On a similar tack, \citet{Feltovich2002} introduce additional noisy type information, finding that this effectively explained counter-intuitive observed behaviour where actors with every right to boast of their quality fail to do so.

\subsection{Normative Decision Theory}

While game theory addresses rational \emph{strategic} decision making, decision theory deals instead with rational decision making \citep{Peterson2009}.  Taken literally, this leads to normative decision theory, where the focus is on giving the rational answer to a decision problem. A complementary view - descriptive, or behavioural decision theory, holds that the focus should instead be on giving an account of human decision making performance, complete with observed deviations from perfect rationality, which we address in section \ref{sub:descriptive_theories}. Finally a third perspective, which to some extent overlaps this division, suggests that decisions are heuristic in nature and rational in ecological context \citep{Gigerenzer1996} (section \ref{sub:heuristic_theories}).

The conceptual underpinning of all of these is the central idea of expected utility, originated by \citet{Bernoulli1954} and later formalised by \citet{Neumann1953}, which simply put, states that the worth of an action is the probability of each outcome, multiplied by the subjective gain or loss it delivers.

Recently, several studies have explored biological correlates to aspects of expected utility. The fundamental concept, that all outcomes are comparable in a universal currency has been supported by evidence of neural correlates of decision variables \citep{Platt1999}, and following from this results from \citet{Padoa-Schioppa2006,Padoa-Schioppa2008} showing neuronal firing in the \ac{OFC} corresponding to revealed preferences in monkeys. Additionally, some support for neural representation of value, and risk aversion was found by \citet{Christopoulos2009}. The model presented in this paper makes an explicit assumption that social decisions utilise the same process, and while this is less well supported there is some evidence to suggest involvement by the same brain region, since damage to the \ac{OFC} has been shown to impair social judgements in both primates \citep{Watson2012}, and humans \citep{Willis2010}.

An alternative normative model of decision making is Bayesian decision theory, proposed by \citet{Robbins1964}, which is essentially the application of Bayesian style probabilities to the expected utility model. This allows probabilities used in reasoning to be subjective, which may allow for a better account of decisions from experience (see \citet{Hertwig2004,Hau2008} for results elucidating the distinction, and comparing the performance of several non-Bayesian models). This model has seen notable successes in practical problems \citep{McNamara1980,Kristensen1997,Survey2003}, but suggestions by several authors  that it could constitute an effective (top-down) model of learning \citep{Tenenbaum2006,Griffiths2010}, or induction \citep{Gallistel2012} in the brain have attracted substantial criticism\footnote{For example \citet{Bowers2012} responding to \citet{Tenenbaum2006}, and \citet{Griffiths2010}; and \citet{Miller2012} addressing \citet{Gallistel2012}.}.

\subsection{Heuristic Decision Making}\label{sub:heuristic_theories}

As noted, heuristic decision making stems from a contention that \citeauthor{Neumann1953} type rationality ignores the context of decision making, and a lack of correspondence between predicted and actual human decisions (see, for example the Allais paradox \citep{Society2013}, and subsequent empirical support from \citet{Burke1996} and \citet{Oliver2003}). Arguably, this notion begins with \citet{Simon1956}, who suggested that humans do not attempt to make optimal choices, but to satisfice and choose the first `good enough' option. While noting that this will often achieve the same result, the claim is that humans exhibit bounded rationality \citep{Simon2000} arising from inherent limits to cognition.

\citet{Gigerenzer1996} take the concept of bounded rationality further, and argue for what they term \acp{FFH}. This recasts rationality as bound to the context of the behaviour: a rational approach to choosing the right mate might well require checking every possible partner, but given finite time, memory, and so on rapidly becomes unachievable. On this basis, they contend that the rationality of any given decision rule can only be determined in the context of the environment \citep{Todd2003}, which implies that heuristics are task specific. They provide a number of heuristics for varying decision problems, e.g. recognition \citep{Goldstein2002}, cue ordering \citep{Gigerenzer1999,Todd2004}, and binary decisions \citep{Brandstatter2006}.

\subsection{Descriptive Decision Theory}\label{sub:descriptive_theories}

While heuristic theories arguably fall under the purview of the descriptive, the wider tendency is towards what are in essence \enquote{patches} to normative models. The most influential models in this class derive from \ac{PT} \citep{Kahneman1979}, which combines a set of heuristics based on observed decision behaviour \citep{Tversky1974}, with distortions to the perception of probability, and the value of outcomes \citep{Kahneman1984,Tversky1986}. \citet{Tversky1992} subsequently addressed issues present in their original formulation by introducing \ac{CPT}, which allows for non-binary decisions, but dispenses with the heuristic aspects of the original formulation. The essence then, is that high and low probabilities are treated differently, and the subjective value of a loss differs from the equivalent gain (losing your shirt is perceived as more of a loss than winning a shirt is a gain).
This last effect, known as the framing effect is particularly significant, see for example work by \citet{Toll2007} examining the relationship between loss and gain framings and success rates in giving up smoking, and \ac{NICE} guidance on framing of treatment options \citep{NICE2007}.

\ac{CPT} has been successful in explaining a number of anomalous results in decision tasks (see \citet{Camerer2004a} for a review), and \citet{Thaler2000} comments to the effect that the theory is promising, albeit incomplete, lacking for example any explanation of how frames are constructed. While remaining an effective account of decision behaviour under risk, the theory does not attempt to resolve apparent inconsistencies that arise when outcomes are delayed, i.e. in situations of intertemporal choice. Historically, \ac{DU} \citep{Samuelson1937}, which effectively claims that the value of a thing now is exponentially greater than the promise of the same thing at some future date, has been applied to explain this. More recently, \citet{Ainslie1991} has suggested that discounting of future outcomes is hyperbolic, rather than exponential. However neither model is complete, in that both fail to account for results from \citet{Thaler1981} showing differing temporal discounting rates for losses and gains. \citet{Loewenstein1992} report additional failings in classic \ac{DU} models, and propose a modified form of \ac{CPT} which they suggest is able to handle both immediate, and intertemporal choice.

>>>>

%!TEX root = disclosure_game.tex
\section{Previous Research}

@@

This section presents a brief overview of literature focusing on the impact
of drinking behaviour in pregnancy, and factors affecting disclosure
behaviour in the midwifery context.

\subsection{Alcohol, and Disclosure in the Maternity Setting}
\label{sub:alcohol_disclosure}

\subsubsection{Impact of Alcohol\label{sub:Impact-of-Alcohol}}

Distinct from stigma attached to alcohol consumption in pregnancy,
is the question of the real impact on woman and baby both in the \gls{antenatal}
period, and beyond. While the canonical example of alcohol linked
disorders is \ac{FAS}, and others on that spectrum, heavy drinking
during pregnancy has been mooted as a factor in a variety of negative
health outcomes.

The impact of moderate alcohol consumption in pregnancy is more contested.
For example, \citet{Andersen2012} examined moderate drinking in a
large Danish cohort study, finding a significant increase in the risk
of spontaneous abortion at low levels of consumption early in pregnancy.
\citet{Savitz2012} questioned the extent to which this can be interpreted
as a causal connection, noting that there is a known relationship
between absence of morning sickness, and spontaneous abortion, and
suggesting that this may explain much of the difference in risk. \citet{Kesmodel2002}
examined the relationship between alcohol consumption and still-birth,
finding that increased consumption lead to an increase in risk to
the baby, but in contrast to \citet{Andersen2012} this was significant
at \gls{term}.

Considering longer term negative outcomes, a metastudy by \citet{Latino-Martel2010}
examined the potential for maternal alcohol consumption in pregnancy
to feature as a risk factor for onset of childhood leukaemia, finding
that any alcohol consumption was associated with an increased risk
of childhood \ac{AML}, but note the rarity of the condition as a
limitation.

\citet{Huizink2006} reviewed literature looking at the impact of
moderate consumption on neurodevelopmental and cognitive outcomes,
concluding that maternal consumption can be a contributing factor
to \ac{ADHD}, and impairments to learning and memory. They subsequently
suggest that the underlying mechanism is not specific to alcohol consumption,
but a more general phenomena arising from perturbations to foetal
conditions \citep{Huizink2009}, but caution that methodological issues
in many of the studies reviewed may undermine this hypothesis.

Contrary to this, a meta-study by \citet{Gray2006} found there was
insufficient evidence to suggest any harm arising from moderate (under
1.5 UK units per day) alcohol consumption. This ties to the current
guidance from the \ac{NICE} \citep{NICE2010a}, advising that women
should avoid drinking at all in at least the first three months of
pregnancy, and no more than 1-2 units once or twice a week if they
do. In giving this advice, \ac{NICE} acknowledge that the risks to
the foetus from alcohol are a somewhat contentious subject, concluding
that the evidence of harm is inconclusive, but that this is not sufficient
to rule out the risk of negative outcomes. This tension is reflected
by earlier guidance from the \ac{RCOG} \citep{Gynecologists1996}
suggesting no evidence of harm below 15 units per week, and subsequent
criticism by \citet{Guerri1999}, who suggest that this might be interpreted
as legitimising \gls{binge}, while noting several studies indicating
adverse affects linked to even a single drink per day (e.g. \citet{Day1990}).
A subsequent \ac{RCOG} statement \citep{RoyalCollegeofObstetriciansandGynaecologists2006}
revised the recommendations to incorporate newer findings, advising
that there is no known safe threshold for drinking in pregnancy, and
highlighting binge drinking as of particular concern.

There has recently been an increased interest in the impact of binge
drinking, as a distinct pattern of consumption, with a wide variety
of negative outcomes reported by \citet{Maier2001}, although a significant
portion of their evidence base is drawn from animal studies which
augers for caution in generalising findings to humans. \citet{Strandberg-larsen2008}
explored links between binge drinking, and stillbirth, reporting a
statistically significant increase in risk associated with more than
three antenatal binge episodes. \citet{Sun2009} looked at seizure
disorders in children whose mothers binged during pregnancy. They
reported significantly greater risk of both neonatal seizures (\textasciitilde{}3
fold) and epilepsy (1.81 fold) associated with binge drinking between
11 and 16 weeks, but emphasised the exploratory nature of the results,
and need for replication. In terms of neurodevelopmental outcomes,
\citet{Streissguth1994} found a dose dependent association with scores
on timed word, and arithmetic tests in fourteen year olds with a stronger
association where bingeing occurred. A review by \citet{Henderson2007}
cautiously supports the contention that binge drinking has a neurodevelopmental
impact, but found no consistent support for adverse outcomes in pregnancy
(e.g. stillbirth, miscarriage, etc.) and note a paucity of studies
in the area. \citet{Meyer-Leu2011} considered the neonatal period,
finding that both moderate and binge drinking were associated with
an increased trend towards neonatal asphyxia. They also noted a large
number of contradictory findings and raising methodological concerns
about the studies reviewed by \citeauthor{Henderson2007}. \citet{Barr2006}
contend that binge drinking may also contribute to psychiatric issues
in the later life of offspring, although in this case their findings
are confined to individuals with \ac{FAS}, which may in itself be
a confounding factor, rather than indicating a directly causative
relationship between antenatal binge drinking and subsequent psychiatric
disorder in offspring.

Overall, there is a distinct lack of consensus on what, and how extensive,
the effects of drinking on the immediate and long term health outcomes
are for the child.

\subsubsection{Disclosure}

The issue of disclosure is central to the model presented here, in
particular self-report by women of information that might disadvantage
them, or be expected to do so in the immediate term. In general, the
consensus is that alcohol self-reports have acceptable validity in
the research context \citep{DelBoca2000}, but do not correspond perfectly
to alternative methods. \citet{DelBoca2003} claim that the validity
is generally accepted, and suggest that the current focus lies on
what factors and processes underlie the discrepancies rather than
questioning determining their existence. In this instance, the conjecture
is that the information is in some way stigmatising; that, following
\citet{Goffman1999}, disclosure equates to revelation of the mark.
This is not immediately contentious, for example \citet{Gomberg1988}
identified stigma surrounding alcohol abusing women in particular,
an issue also highlighted by \ac{IAPT} guidance \citep{IAPT2012},
as well as a number of other studies relating response effects to
perceived negative consequences \citep{Langenbucher2001,DelBoca2000,Blair1977}.
In the maternity context, \citet{Radcliffe2011} identifies stigma
pertaining to substance misusing women amongst staff, and suggests
that this may represent a barrier to appropriate treatment; similarly,
\ac{NICE} guidance on pregnancy and complex social factors \citep{NICE2010}
recognises concern about the attitude of staff as a source of anxiety
in pregnant women who misuse substances.

Stigma, or fear of a judgemental response on the part of the practitioner
should not however be taken uncritically to explain inaccurate reporting
by patients. While recent \ac{NICE} public health guidance advocates
routine alcohol misuse screening as a part of all practice \citep{NationalInstituteforHealthandCareExcellence2010},
there is no specific policy for routine antenatal care beyond providing
information on possible impacts of alcohol consumption \citep{NICE2010a}.
\ac{NICE} guidance on pregnancy and complex social factors \citep{NICE2010}
does specifically address women who misuse alcohol, but presupposes
knowledge of the problem through medical history, or via other services.
Taken in concert with the potential for harm from even moderate alcohol
use (section \ref{sub:Impact-of-Alcohol}), this suggests that much
of the onus is on the patient to volunteer information.

Where screening is used, \citet{Kaskutas2000} note that the most
basic method, i.e. number of standard drinks consumed, can lead to
inaccurate estimates of consumption arising from inability to relate
the concept of a standard drink, to actual consumption. This is compounded
by the impact of memory effects on recall over a number of days \citep{Stockwell2004},
and a lack of consistency in the standard drink measure \citep{Turner1990}.
Alternative screening tools, for example \acs{AUDIT}, and \acs{T-ACE}
are available and have been shown to perform well in identifying problematic
levels of drinking \citep{Piccinelli1997,Bradley1998,Russell1994,Russell1996},
although the emphasis in these cases is on consumption at disordered
levels.

\citet{Prior2003} considered a different health arena (mental health
problems and GPs), with similar characteristics in terms of concealment
of medically relevant information. The central finding in this case
is that non-disclosure is not a result of stigma, but of mismatched
ontologies surrounding mental illness. Work by \citet{Alvik2005},
where the relationship between anonymity and reporting of alcohol
consumption by pregnant women was investigated, found no significant
relationship, suggesting that a fear of social judgement may not be
a dominant factor. This draws an interesting contrast with a study
by \citet{Alvik2006}, which found that contemporaneous reports of
consumption were significantly lower than those postpartum. Logistic
regression results suggest that this trend is amplified by a number
of factors, including level of alcohol consumption preceding conception,
while anxiety about foetal wellbeing during pregnancy was associated
with lower retrospective reports. Taken together with \citep{Alvik2005},
these results could be seen as conflicting, but may suggest self-stigmatisation
\citep{Watson2007}, or reflect a lack of distinction between anonymity,
and confidentiality \citep{Malvin1983}.

In summation then, there is a consensus that alcohol consumption is
generally underreported in the pregnant population, with some support
for the idea that concern about social judgement associated with stigmatisation
may be a contributing factor. Of particular interest in the wider
context of this work, is the relationship between underreporting and
consumption, i.e. that heavier drinking is associated with a greater
tendency to understate intake.

\subsubsection{Practice Implications}

Given that alcohol consumption is thought to be underreported some
consideration must be given to the implications for midwifery practice,
in terms of eliciting more accurate self-reporting. \citet{Phillips2007}
present a qualitative account of factors influencing the disclosure
of substance misuse to midwives, identifying particularly the need
to build up a rapport, potentially over a number of appointments.
This was related to continuity of care, seen as necessary by both
midwives and women for building up a trust relationship, itself a
key component of facilitating disclosure. \citet{Stevens2002} looked
specifically at the process of transitioning to a caseloading model
of care provision in one midwifery practice, reporting that both practitioners
and women felt that this offered advantages in terms of long term
relationship building. Relationship building was also highlighted
by \citet{Kennedy2004} in a narrative investigation of midwifery
practice, where the subjects interpreted the midwife-woman dynamic
as about mutuality. \citeauthor{Kennedy2004} suggest that this arises
from a recognition that interactions in this context are about information
exchange, with the knowledge base of the woman as significant as that
of the midwife, rather than simply a unidirectionally didactic relationship.

\citet{Hunter2006} also focuses on much of midwifery as about relationship
building, suggesting that there is an insufficiently recognised emotional
labour component to practice. Observation and interview of a number
of midwives as they practiced suggested that many midwives effectively
took a mother type role to their patients, with implications around
the nature of information exchange that was able to take place. The
emotional labour component was also reported by \citeauthor{Stevens2002},
who suggest that this is more evident under a caseloading system, particularly
with challenging patients with complex needs. \citet{Todd1998} surveyed
midwives working in a hospital environment, as well as those working
in the community in a caseloading context, finding that community
practice appeared to provide more job satisfaction, but was challenging
to implement effectively because of limited resources. Community midwives
suggested that larger team sizes, and smaller caseloads would contribute
to a better realisation of the model. \citet{Farquhar2000} approached
the same question from the perspective of women, also finding that
faulty implementation hampered the expected benefits. They found that
those cared for under a team scheme, with much higher continuity of
care, reported that they had a better relationship with their midwives,
but were not more satisfied in general with their care. In contrast,
\citet{Biro2003} looked at a \ac{RCT} of team midwifery care versus
hospital care in Australia, finding a significantly higher level of
satisfaction under the team model, the distinction in this case may
lie in the different balance of team size to caseload size.

In terms of the impact of continuity of care on health, rather than
experiential outcomes, research is relatively sparse. \citet{Marks2003}
examined the impact of continuity of care on \ac{PND}, which has
similar features to alcohol in that it carries an associated stigma
that can act as a barrier to help seeking \citep{Dennis2006}. Based
on the results of a \ac{RCT}, they conclude that continuity of care
is not protective, in the sense of reducing rates or impacting onset,
but was very successful in supporting engagement with treatment. Echoing
this, a 2009 Cochrane Review by \citet{Hatem2009} found no significant
difference in incidence of \ac{PND}, but reported benefits in terms
of lower rates of \gls{episiotomies}, anaesthesia, and shorter hospital
stays, with higher satisfaction as found by \citeauthor{Biro2003}.
While research in this area does not specifically pertain to disclosure,
the general trend in results are suggestive when taken in concert
with studies emphasising the importance of relationship building as
key in fostering a disclosure friendly environment. Continuity of
care is generally regarded as improving patient experience, and leading
to better health outcomes in the wider medical arena \citep{VanWalraven2010},
but is clearly not a cost free endeavour, with particular concern
arising from the emotional cost \citep{Todd1998}, and increased rates
of `\gls{burnout}' in practitioners \citep{Sandall1997}.
